Data analysis for employee cluster descriptive statistics

### 2023-08-22 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
More descriptions

Employees that report to the job site for most days (~97). Some days (~22) telework. Many days co-located with at least one team member (~74), supervisor (~60), or whole team (~17), but high variance. Few days (~4) where the whole team is remote, but high variance. Many working days (~119). Team is smaller (~5)

Clusters 5(5): **Non-workers**
Low number of days (~5) reporting to the site, but high variance. Some days (~27) telework, but high variance. Few days co-located with at least one team member (2)  or with supervisor (~1). Almost no days (<1) with the whole team co-located. Several days (~9) where the entire team works remotely. Few working days (~34) and high variance. Team is large (~9) and high variance.

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

@@

#### Grade

@@

#### Occupational series

```{r}
level_10 <- 
  d %>% 
  count(occupational_series) %>% 
  arrange(desc(n)) %>% 
  slice(10) %>% 
  pull(n)

d %>%
  mutate(occupational_series = fct_lump_min(occupational_series, min = level_10)) %>%
  group_by(.cluster_2) %>%
  count(occupational_series) %>%
  ungroup() %>%
  left_join(d %>%
              count(.cluster_2, name = "tot")) %>%
  mutate(prop = n / tot) %>%
  ggplot(aes(x = .cluster_2, y =  prop, fill = .cluster_2)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(occupational_series), scales = "free_y")
```

```{r}
level_10 <- 
  d %>% 
  count(occupational_series) %>% 
  arrange(desc(n)) %>% 
  slice(10) %>% 
  pull(n)

d %>%
  mutate(occupational_series = fct_lump_min(occupational_series, min = level_10)) %>%
  group_by(.cluster_5) %>%
  count(occupational_series) %>%
  ungroup() %>%
  left_join(d %>%
              count(.cluster_5, name = "tot")) %>%
  mutate(prop = n / tot) %>%
  ggplot(aes(x = .cluster_5, y =  prop, fill = .cluster_5)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(occupational_series), scales = "free_y")
```

#### Position title

```{r}
level_10 <- 
  d %>% 
  count(position_title) %>% 
  arrange(desc(n)) %>% 
  slice(10) %>% 
  pull(n)

d %>%
  mutate(position_title = fct_lump_min(position_title, min = level_10)) %>%
  group_by(.cluster_2) %>%
  count(position_title) %>%
  ungroup() %>%
  left_join(d %>%
              count(.cluster_2, name = "tot")) %>%
  mutate(prop = n / tot) %>%
  ggplot(aes(x = .cluster_2, y =  prop, fill = .cluster_2)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(position_title), scales = "free_y", ncol = 3) +
  theme(
    legend.position = "none"
  )
```

```{r}
level_10 <- 
  d %>% 
  count(position_title) %>% 
  arrange(desc(n)) %>% 
  slice(10) %>% 
  pull(n)

d %>%
  mutate(position_title = fct_lump_min(position_title, min = level_10)) %>%
  group_by(.cluster_5) %>%
  count(position_title) %>%
  ungroup() %>%
  left_join(d %>%
              count(.cluster_5, name = "tot")) %>%
  mutate(prop = n / tot) %>%
  ggplot(aes(x = .cluster_5, y =  prop, fill = .cluster_5)) +
  geom_col(position = "dodge")  +
   facet_wrap(facets = vars(position_title), scales = "free_y", ncol = 3) +
  theme(
    legend.position = "none"
  )
```

#### State

```{r}
level_10 <- 
  d %>% 
  count(location_state) %>% 
  arrange(desc(n)) %>% 
  slice(10) %>% 
  pull(n)

d %>%
  mutate(location_state = fct_lump_min(location_state, min = level_10)) %>%
  group_by(.cluster_2) %>%
  count(location_state) %>%
  ungroup() %>%
  left_join(d %>%
              count(.cluster_2, name = "tot")) %>%
  mutate(prop = n / tot) %>%
  ggplot(aes(x = .cluster_2, y =  prop, fill = .cluster_2)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(location_state), scales = "free_y")
```

```{r}
level_10 <- 
  d %>%
  count(location_state) %>% 
  arrange(desc(n)) %>% 
  slice(10) %>% 
  pull(n)

d %>%
  mutate(location_state = fct_lump_min(location_state, min = level_10)) %>%
  group_by(.cluster_5) %>%
  count(location_state) %>%
  ungroup() %>%
  left_join(d %>%
              count(.cluster_5, name = "tot")) %>%
  mutate(prop = n / tot) %>%
  ggplot(aes(x = .cluster_5, y =  prop, fill = .cluster_5)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(location_state), scales = "free_y")
```

#### City, State

```{r}
level_10 <- 
  d %>% 
  unite(loc, location_city, location_state, sep = ", ") %>% 
  count(loc) %>% 
  arrange(desc(n)) %>% 
  slice(15) %>% 
  pull(n)

d %>%
  unite(loc, location_city, location_state, sep = ", ") %>% 
  mutate(loc = fct_lump_min(loc, min = level_10)) %>%
  group_by(.cluster_2) %>%
  count(loc) %>%
  ungroup() %>%
  left_join(d %>%
              count(.cluster_2, name = "tot")) %>%
  mutate(prop = n / tot) %>%
  ggplot(aes(x = .cluster_2, y =  prop, fill = .cluster_2)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(loc), scales = "free_y")
```

```{r}
level_10 <- 
  d %>%
  unite(loc, location_city, location_state, sep = ", ") %>% 
  count(loc) %>% 
  arrange(desc(n)) %>% 
  slice(15) %>% 
  pull(n)

d %>%
  unite(loc, location_city, location_state, sep = ", ") %>% 
  mutate(loc = fct_lump_min(loc, min = level_10)) %>%
  group_by(.cluster_5) %>%
  count(loc) %>%
  ungroup() %>%
  left_join(d %>%
              count(.cluster_5, name = "tot")) %>%
  mutate(prop = n / tot) %>%
  ggplot(aes(x = .cluster_5, y =  prop, fill = .cluster_5)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(loc), scales = "free_y")
```

@@

More often located in the states of Georgia, Illinois, Maryland, Pennsylvania, and Virginia, and in the cities of Alexandria (VA), Arlington (VA), Atlanta (GA), Auburn (WA), Chicago (IL), Fort Worth (TX), Philadelphia (PA), San Diego (CA), and San Francisco (CA).

Primarily Grades 13, 14, and 15.

Higher proportion in series 0301 (Miscellaneous Administration and Program Series), 0343 (Management and Program Analysis Series), 0501 (Financial Administration and Program Series), 0560 (Budget Analysis Series), 1102 (Contracting Series), 1170 (Realty Series), 2150 (Transportation Operations Series), and 2210 (Information Technology Management Series).

More likely to be Budget Analysts, Contract Specialists, Program Analysts, Realty Specialists, Supervisory Contract Specialists, Transportation Operations Specialists, and other less common series.

@@

More often located in DC, and less common states, and in the cities of Boston (MA), Kansas City (MO), Los Angeles (CA), and Washington DC.

Primarily in Grades below 13.

Higher proportion in series 1176 (Building Management Series).

More likely to be Building Management Specialists, Building Managers, and Construction Control Representatives.

@@

More often located in the states of Georgia, Maryland, Missouri, New York, Pennsylvania, and Virginia, and in the cities of Alexandria (VA), New York (NY), and Philadelphia (PA).

Higher proportions in Grades 13, 14, and 15.

Higher proportion in series 0343 (Management and Program Analysis Series), 0501 (Financial Administration and Program Series), 0560 (Budget Analysis Series), 1102 (Contracting Series), and 2210 (Information Technology Management Series).

More likely to be Budget Analysts, Contract Specialists, Program Analysts, and Supervisory Constract Specialists.

@@

More often located in the states of Georgia, Illinois, Maryland, and Virginia, and in the cities of Alexandria (VA), Arlington (VA), and San Diego (CA).

Higher proportions in Grades 13, 14, and 15.

Higher proportion in series series 0343 (Management and Program Analysis Series), 0501 (Financial Administration and Program Series), 0560 (Budget Analysis Series), 1102 (Contracting Series), and 2210 (Information Technology Management Series).

More likely to be Budget Analysts, Contract Specialists, Program Analysts, Realty Specialists, and Supervisory Constract Specialists.

@@

More often located in the states of California, Georgia, Illinois, and DC, and in the cities of Atlanta (GA), Auburn (WA), Boston (MA), Chicago (IL), Kansas City (MO), Lakewood (CO),  Los Angeles (CA), San Diego (CA), San Francisco (CA) and Washington DC.

Higher proportions in Grades 00 and 13.

Higher proportion in series 1101 (General Business and Industry Series), 1170 (Realty Series), 2150 (Transportation Operations Series), and other less common series.

More likely to be Construction Control Representatives, Program Managers, Realty Specialists, and Transportation Operations Specialists.

@@

More often located in the states of New York, DC, and less common states, and in the cities of Los Angeles (CA), and Washington DC.

Higher proportions in Grades 05, 11, 12, and other grades with few people in them.

Higher proportion in series in series 1176 (Building Management Series).

More likely to be Building Management Specialists, Building Managers, and Construction Control Representatives.

@@

More often located in DC, and in the cities of Alexandria (VA), Arlington (VA), and Washington DC.

Higher proportions in Grades 04, 15, and other grades with few people in them.

Higher proportion in series 0301 (Miscellaneous Administration and Program Series), but common in all series.

Fairly dispersed across position titles.
